Matching Bullets

### 2015-12-01 imaging-paper.Rnw
bullet-stats.csv updated

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=10.5, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, 
             data = filter(db1, part==1, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Part 1 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlaid.\label{fig:circlefits}}%
\end{figure}

@@

<<loess_fit, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit for part 1 of bullet 1', fig.pos='hbtp', message=FALSE>>=

@@

my.loess$fitted
@

<<loess_resid, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Loess fit residuals for part 1 of bullet 1', fig.pos='hbtp'>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

my.loess$resid
@

We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from part 1 of bullet 1. This is available in Figure \ref{fig:loessfits}.

<<loessfits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
br121.groove <- get_grooves(br121_bullet)
br122.groove <- get_grooves(br122_bullet)
br123.groove <- get_grooves(br123_bullet)
br124.groove <- get_grooves(br124_bullet)
br125.groove <- get_grooves(br125_bullet)
br126.groove <- get_grooves(br126_bullet)

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1) + ggtitle("Part 1 of Bullet 1 in black")
@

>>>>

\begin{figure}[hbtp]
  \centering
<<circlefits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=2) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, 
             data = filter(db1, part==1, x == 100)[,c("y", "resid", "x")]) +
  ylab("Residuals from circular fit") +
  ggtitle("Part 1 of Bullet 1 in black")
@
\caption{Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlaid.\label{fig:circlefits}}%
\end{figure}

@@

\begin{figure}[hbtp]
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_fit} Loess fit for land 1 of bullet 1.}
<<loess_fit, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE,  message=FALSE>>=

@@

my.loess$fitted
@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{\label{fig:loess_resid} Loess fit residuals for land 1 of bullet 1.}
<<loess_resid, echo=FALSE, fig.width=10, fig.height=3.5, out.width='\\linewidth', warning=FALSE>>=
my.loess <- fit_loess(br111_bullet, br111.groove)

my.loess$resid
@
\end{subfigure}
\caption{Fit and residuals of a loess fit to land 1 of bullet 1 (Barrel 1).}
\end{figure}

We can reproduce a similar figure to the one from the circular fits by overlaying the residuals from each loess fit for bullet 2 onto an image of the loess residuals from part 1 of bullet 1. This is shown in Figure~\ref{fig:loessfits}.

\begin{figure}[hbtp]
<<loessfits, echo=FALSE, fig.width=7, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
br121.groove <- get_grooves(br121_bullet)
br122.groove <- get_grooves(br122_bullet)
br123.groove <- get_grooves(br123_bullet)
br124.groove <- get_grooves(br124_bullet)
br125.groove <- get_grooves(br125_bullet)
br126.groove <- get_grooves(br126_bullet)

@@

qplot(y, resid, data=melt.df, #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey70")) + 
  facet_wrap(~part, ncol=3) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(data = actual.df, aes(y, resid), colour="black", size=1) + ggtitle("Land 1 of Bullet 1 in black")
@    
\caption{Residuals of a loess fit to bullets 1 and 2 from barrel 1. Land 1 of bullet 1 is shown in black. }
\end{figure}
